```{r}
library(tidyverse)
```

---

```{r}
load("~/rproj/Paper3Annot_2024/ClinVar20240107/20240219_ClinVar_VCF/df_clinvar_GRCh37_BLB_Tx1.RData")
load("~/rproj/Paper3Annot_2024/ClinVar20240107/20240219_ClinVar_VCF/df_clinvar_GRCh37_PLP_Tx1.RData")
load("~/rproj/Paper3Annot_2024/ClinVar20240107/20240219_ClinVar_VCF/df_clinvar_GRCh38_BLB_Tx1.RData")
load("~/rproj/Paper3Annot_2024/ClinVar20240107/20240219_ClinVar_VCF/df_clinvar_GRCh38_PLP_Tx1.RData")
```

---

```{r}
df_clinvar_GRCh37_PLP_Tx1 %>%
  group_by(ClinVar_CLNSIG) %>%
  count()
```

```{r}
df_clinvar_GRCh37_BLB_Tx1 %>%
  group_by(ClinVar_CLNSIG) %>%
  count()
```

```{r}
df_clinvar_GRCh38_PLP_Tx1 %>%
  group_by(ClinVar_CLNSIG) %>%
  count()
```

```{r}
df_clinvar_GRCh38_BLB_Tx1 %>%
  group_by(ClinVar_CLNSIG) %>%
  count()
```

---

```{r}
df_clinvar_GRCh37_PLP_Tx1 %>%
  select(chr, start, ref, alt, VariationID, AlleleID) %>%
  # mutate(key = str_c(VariationID, AlleleID, sep = "|")) %>%
  rename(`#CHROM` = chr, POS = start, REF = ref, ALT = alt) %>%
  mutate(ID = ".", QUAL = ".", FILTER = ".") %>%
  mutate(FORMAT = 'GT:AD:DP') %>%
  mutate(ClinVarg37 = "1/1:0,100:100") %>%
  mutate(INFO = str_c("TAG=", key)) %>%
  select(
    `#CHROM`,
    POS,
    ID,
    REF,
    ALT,
    QUAL,
    FILTER,
    INFO,
    FORMAT,
    ClinVarg37
  ) %>%
  write_tsv(file = "ClinVar_GRCh37_PLP_Tx1_20240107.mvcf")

# 44,351
```

```{r}
df_clinvar_GRCh37_BLB_Tx1 %>%
  select(chr, start, ref, alt, VariationID, AlleleID) %>%
  # mutate(key = str_c(VariationID, AlleleID, sep = "|")) %>%
  rename(`#CHROM` = chr, POS = start, REF = ref, ALT = alt) %>%
  mutate(ID = ".", QUAL = ".", FILTER = ".") %>%
  mutate(FORMAT = 'GT:AD:DP') %>%
  mutate(ClinVarg37 = "1/1:0,100:100") %>%
  mutate(INFO = str_c("TAG=", key)) %>%
  select(
    `#CHROM`,
    POS,
    ID,
    REF,
    ALT,
    QUAL,
    FILTER,
    INFO,
    FORMAT,
    ClinVarg37
  ) %>%
  write_tsv(file = "ClinVar_GRCh37_BLB_Tx1_20240107.mvcf")

# 120,265
```

```{r}
df_clinvar_GRCh38_PLP_Tx1 %>%
  select(chr, start, ref, alt, VariationID, AlleleID) %>%
  # mutate(key = str_c(VariationID, AlleleID, sep = "|")) %>%
  rename(`#CHROM` = chr, POS = start, REF = ref, ALT = alt) %>%
  mutate(ID = ".", QUAL = ".", FILTER = ".") %>%
  mutate(FORMAT = 'GT:AD:DP') %>%
  mutate(ClinVarg37 = "1/1:0,100:100") %>%
  mutate(INFO = str_c("TAG=", key)) %>%
  select(
    `#CHROM`,
    POS,
    ID,
    REF,
    ALT,
    QUAL,
    FILTER,
    INFO,
    FORMAT,
    ClinVarg37
  ) %>%
  write_tsv(file = "ClinVar_GRCh38_PLP_Tx1_20240107.mvcf")

# 44,351
```

```{r}
df_clinvar_GRCh38_BLB_Tx1 %>%
  select(chr, start, ref, alt, VariationID, AlleleID) %>%
  # mutate(key = str_c(VariationID, AlleleID, sep = "|")) %>%
  rename(`#CHROM` = chr, POS = start, REF = ref, ALT = alt) %>%
  mutate(ID = ".", QUAL = ".", FILTER = ".") %>%
  mutate(FORMAT = 'GT:AD:DP') %>%
  mutate(ClinVarg37 = "1/1:0,100:100") %>%
  mutate(INFO = str_c("TAG=", key)) %>%
  select(
    `#CHROM`,
    POS,
    ID,
    REF,
    ALT,
    QUAL,
    FILTER,
    INFO,
    FORMAT,
    ClinVarg37
  ) %>%
  write_tsv(file = "ClinVar_GRCh38_BLB_Tx1_20240107.mvcf")

# 120,198
```

---

```{bash}

cat vcf_header.txt ClinVar_GRCh37_PLP_Tx1_20240107.mvcf > ClinVar_GRCh37_PLP_Tx1_20240107.vcf
rm ClinVar_GRCh37_PLP_Tx1_20240107.mvcf

cat vcf_header.txt ClinVar_GRCh37_BLB_Tx1_20240107.mvcf > ClinVar_GRCh37_BLB_Tx1_20240107.vcf
rm ClinVar_GRCh37_BLB_Tx1_20240107.mvcf

cat vcf_header.txt ClinVar_GRCh38_PLP_Tx1_20240107.mvcf > ClinVar_GRCh38_PLP_Tx1_20240107.vcf
rm ClinVar_GRCh38_PLP_Tx1_20240107.mvcf

cat vcf_header.txt ClinVar_GRCh38_BLB_Tx1_20240107.mvcf > ClinVar_GRCh38_BLB_Tx1_20240107.vcf
rm ClinVar_GRCh38_BLB_Tx1_20240107.mvcf

```

---

```{bash}
# bcftools pod

cd /volume/rproj/Paper3Annot_2024/ClinVar20240107/20240219_ClinVar_VCF

bgzip -k ClinVar_GRCh37_PLP_Tx1_20240107.vcf
bgzip -k ClinVar_GRCh37_BLB_Tx1_20240107.vcf
bgzip -k ClinVar_GRCh38_PLP_Tx1_20240107.vcf
bgzip -k ClinVar_GRCh38_BLB_Tx1_20240107.vcf

bcftools index ClinVar_GRCh37_PLP_Tx1_20240107.vcf.gz
bcftools index ClinVar_GRCh37_BLB_Tx1_20240107.vcf.gz
bcftools index ClinVar_GRCh38_PLP_Tx1_20240107.vcf.gz
bcftools index ClinVar_GRCh38_BLB_Tx1_20240107.vcf.gz

```

---

```{bash}
# bcftools pod

bcftools stats ClinVar_GRCh37_PLP_Tx1_20240107.vcf.gz

```
number of records:      44351
number of no-ALTs:      0
number of SNPs:         29391
number of MNPs:         130
number of indels:       14830
number of others:       0

```{bash}
# bcftools pod

bcftools stats ClinVar_GRCh37_BLB_Tx1_20240107.vcf.gz

```
number of records:      120265
number of no-ALTs:      0
number of SNPs:         115337
number of MNPs:         140
number of indels:       4788
number of others:       0

```{bash}
# bcftools pod

bcftools stats ClinVar_GRCh38_PLP_Tx1_20240107.vcf.gz

```
number of records:      44351
number of no-ALTs:      0
number of SNPs:         29391
number of MNPs:         130
number of indels:       14830
number of others:       0

```{bash}
# bcftools pod

bcftools stats ClinVar_GRCh38_BLB_Tx1_20240107.vcf.gz

```
number of records:      120198
number of no-ALTs:      0
number of SNPs:         115269
number of MNPs:         139
number of indels:       4790
number of others:       0





