```{r}
library(tidyverse)
```

```{bash}
head -n 40 GRCh38_BLB/ClinVar_GRCh38_BLB_Tx1_20240107.vep.vcf
```
Allele|Consequence|IMPACT|SYMBOL|Gene|Feature_type|Feature|BIOTYPE|EXON|INTRON|HGVSc|HGVSp|cDNA_position|CDS_position|Protein_position|Amino_acids|Codons|Existing_variation|DISTANCE|STRAND|FLAGS|VARIANT_CLASS|SYMBOL_SOURCE|HGNC_ID|CANONICAL|MANE_SELECT|MANE_PLUS_CLINICAL|ENSP|REFSEQ_MATCH|REFSEQ_OFFSET|GIVEN_REF|USED_REF|BAM_EDIT|HGVS_OFFSET|HGVSg

```{r}
tsv_query <- read_tsv(
  file("GRCh38_BLB/ClinVar_GRCh38_BLB_Tx1_20240107.query.tsv"), 
  col_names = c(
    "chr",
    "start",
    "ref",
    "alt",
    "key",
    "Allele",
    "Consequence",
    "IMPACT",
    "SYMBOL",
    "Gene",
    "Feature_type",
    "Feature",
    "BIOTYPE",
    "EXON",
    "INTRON",
    "HGVSc",
    "HGVSp",
    "cDNA_position",
    "CDS_position",
    "Protein_position",
    "Amino_acids",
    "Codons",
    "Existing_variation",
    "DISTANCE",
    "STRAND",
    "FLAGS",
    "VARIANT_CLASS",
    "SYMBOL_SOURCE",
    "HGNC_ID",
    "CANONICAL",
    "MANE_SELECT",
    "MANE_PLUS_CLINICAL",
    "NP",
    "REFSEQ_MATCH",
    "REFSEQ_OFFSET",
    "GIVEN_REF",
    "USED_REF",
    "BAM_EDIT",
    "HGVS_OFFSET",
    "HGVSg"
  ),
  col_types = cols(start = col_number(), .default = col_character())
)
```

```{r}
df_ClinVar_GRCh38_BLB_vep_refseq <- tsv_query %>%
  select(
    key, chr, start, ref, alt,
    VARIANT_CLASS, SYMBOL, Consequence, IMPACT,
    Gene, Feature, Feature_type, BIOTYPE, STRAND, FLAGS,
    EXON, INTRON, cDNA_position, CDS_position, DISTANCE,
    NP, Protein_position, Amino_acids, Codons,
    HGVSg, HGVSc, HGVSp,
    CANONICAL, MANE_SELECT, MANE_PLUS_CLINICAL, HGVS_OFFSET
  ) %>%
  mutate(NM = str_extract(Feature, '[^\\.]+'))
```

---

```{r}
df_ClinVar_GRCh38_BLB_vep_refseq %>%
  mutate(NM = str_extract(Feature, '\\w.')) %>%
  group_by(NM) %>%
  count()
```

# 只留NM, NR, NC Tx
```{r}
df_ClinVar_GRCh38_BLB_vep_refseq <- df_ClinVar_GRCh38_BLB_vep_refseq %>%
  filter(str_detect(NM, '^N\\w_[0-9]+'))
```

---

```{r}
save(df_ClinVar_GRCh38_BLB_vep_refseq, file = "GRCh38_BLB/df_ClinVar_GRCh38_BLB_vep_refseq.RData")
```







