```{r}
library(tidyverse)
```

```{r}
load("~/rproj/Paper3Annot_2024/ClinVar20240107/20240226_refseq_vep/GRCh37_BLB/df_ClinVar_GRCh37_BLB_vep_refseq.RData")
load("~/rproj/Paper3Annot_2024/ClinVar20240107/20240226_refseq_vep/GRCh37_PLP/df_ClinVar_GRCh37_PLP_vep_refseq.RData")
```

---

```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(Consequence) %>%
  separate_rows(Consequence, sep = "&") %>%
  group_by(Consequence) %>%
  count() %>%
  arrange(Consequence)

```

---

# NMD_transcript_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "NMD_transcript_variant"))
```
沒有

# stop_retained_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "stop_retained_variant"))
```
伴隨3_prime_UTR_variant時沒有HGVSp
太難搞，Others

# start_retained_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "start_retained_variant"))
```
沒有

# incomplete_terminal_codon_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "incomplete_terminal_codon_variant"))
```
沒有

# protein_altering_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "protein_altering_variant"))
```
兩種組合出現
protein_altering_variant&splice_region_variant
stop_gained&protein_altering_variant
都有HGVSp
太難搞，Others

# coding_sequence_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "coding_sequence_variant"))
```
有些有HGVSp
太難搞，Others

# non_coding_transcript_exon_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "non_coding_transcript_exon_variant"))
```
沒有HGVSp

# non_coding_transcript_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "non_coding_transcript_variant"))
```
沒有HGVSp

# splice_polypyrimidine_tract_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "splice_polypyrimidine_tract_variant"))
```
當intron_variant

# splice_donor_5th_base_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "splice_donor_5th_base_variant"))
```
當intron_variant

# mature_miRNA_variant
```{r}
bind_rows(
  df_ClinVar_GRCh37_BLB_vep_refseq,
  df_ClinVar_GRCh37_PLP_vep_refseq
) %>%
  select(key, NM, Consequence, HGVSc, HGVSp) %>%
  filter(str_detect(Consequence, "mature_miRNA_variant"))
```
沒有

---

# Concordance

```{r}
CSQ_ClinVar_GRCh37_BLB_vep_refseq <- df_ClinVar_GRCh37_BLB_vep_refseq %>%
  mutate(
    Consequence = case_when(
      
      str_detect(Consequence, "splice_acceptor_variant") ~ "splicing_variant",
      str_detect(Consequence, "splice_donor_variant") ~ "splicing_variant",
      
      str_detect(Consequence, "stop_gained") ~ "nonsense",
      
      str_detect(Consequence, "frameshift_variant") ~ "frameshift_variant",
      
      str_detect(Consequence, "stop_lost") ~ "stop_lost",
      str_detect(Consequence, "start_lost") ~ "initiatior_codon_variant",
      
      str_detect(Consequence, "inframe_") ~ "inframe_variant",
      
      str_detect(Consequence, "missense_variant") ~ "missense_variant",
      
      str_detect(Consequence, "synonymous_variant") ~ "synonymous_variant",

      str_detect(Consequence, "5_prime_UTR_variant") ~ "5_prime_UTR_variant",
      str_detect(Consequence, "3_prime_UTR_variant") ~ "3_prime_UTR_variant",
      
      str_detect(Consequence, "non_coding_transcript_exon_variant") ~ "non_coding_transcript_variant",
      str_detect(Consequence, "non_coding_transcript_variant") ~ "non_coding_transcript_variant",
      
      str_detect(Consequence, "protein_altering_variant") ~ "Others",
      str_detect(Consequence, "coding_sequence_variant") ~ "Others",
      str_detect(Consequence, "stop_retained_variant") ~ "Others",
      str_detect(Consequence, "incomplete_terminal_codon_variant") ~ "Others",
      str_detect(Consequence, "start_retained_variant") ~ "Others",
      
      str_detect(Consequence, "intron_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_donor_5th_base_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_region_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_donor_region_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_polypyrimidine_tract_variant") ~ "intron_variant",
      
      str_detect(Consequence, "upstream_gene_variant") ~ "genic_upstream_transcript_variant",
      str_detect(Consequence, "downstream_gene_variant") ~ "genic_downstream_transcript_variant",
      
      str_detect(Consequence, "intergenic_variant") ~ "intergenic_variant",
      
      TRUE ~ "Others"
      
    )
  ) %>%
  select(key, Feature, Consequence) %>%
  mutate(NM = str_extract(Feature, '[^\\.]+'))
```

```{r}
save(CSQ_ClinVar_GRCh37_BLB_vep_refseq, file = "CSQ_concordance/CSQ_ClinVar_GRCh37_BLB_vep_refseq.RData")
```


```{r}
CSQ_ClinVar_GRCh37_PLP_vep_refseq <- df_ClinVar_GRCh37_PLP_vep_refseq %>%
  mutate(
    Consequence = case_when(
      
      str_detect(Consequence, "splice_acceptor_variant") ~ "splicing_variant",
      str_detect(Consequence, "splice_donor_variant") ~ "splicing_variant",
      
      str_detect(Consequence, "stop_gained") ~ "nonsense",
      
      str_detect(Consequence, "frameshift_variant") ~ "frameshift_variant",
      
      str_detect(Consequence, "stop_lost") ~ "stop_lost",
      str_detect(Consequence, "start_lost") ~ "initiatior_codon_variant",
      
      str_detect(Consequence, "inframe_") ~ "inframe_variant",
      
      str_detect(Consequence, "missense_variant") ~ "missense_variant",
      
      str_detect(Consequence, "synonymous_variant") ~ "synonymous_variant",

      str_detect(Consequence, "5_prime_UTR_variant") ~ "5_prime_UTR_variant",
      str_detect(Consequence, "3_prime_UTR_variant") ~ "3_prime_UTR_variant",
      
      str_detect(Consequence, "non_coding_transcript_exon_variant") ~ "non_coding_transcript_variant",
      str_detect(Consequence, "non_coding_transcript_variant") ~ "non_coding_transcript_variant",
      
      str_detect(Consequence, "protein_altering_variant") ~ "Others",
      str_detect(Consequence, "coding_sequence_variant") ~ "Others",
      str_detect(Consequence, "stop_retained_variant") ~ "Others",
      str_detect(Consequence, "incomplete_terminal_codon_variant") ~ "Others",
      str_detect(Consequence, "start_retained_variant") ~ "Others",
      
      str_detect(Consequence, "intron_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_donor_5th_base_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_region_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_donor_region_variant") ~ "intron_variant",
      str_detect(Consequence, "splice_polypyrimidine_tract_variant") ~ "intron_variant",
      
      str_detect(Consequence, "upstream_gene_variant") ~ "genic_upstream_transcript_variant",
      str_detect(Consequence, "downstream_gene_variant") ~ "genic_downstream_transcript_variant",
      
      str_detect(Consequence, "intergenic_variant") ~ "intergenic_variant",
      
      TRUE ~ "Others"
      
    )
  ) %>%
  select(key, Feature, Consequence) %>%
  mutate(NM = str_extract(Feature, '[^\\.]+'))
```

```{r}
save(CSQ_ClinVar_GRCh37_PLP_vep_refseq, file = "CSQ_concordance/CSQ_ClinVar_GRCh37_PLP_vep_refseq.RData")
```




