```{r}
library(tidyverse)
```

```{bash}
head -n 40 GRCh37_BLB/ClinVar_GRCh37_BLB_Tx1_20240107.snpeff.vcf
```
Allele | Annotation | Annotation_Impact | Gene_Name | Gene_ID | Feature_Type | Feature_ID | Transcript_BioType | Rank | HGVS.c | HGVS.p | cDNA.pos / cDNA.length | CDS.pos / CDS.length | AA.pos / AA.length | Distance | ERRORS / WARNINGS / INFO
Gene_Name | Gene_ID | Number_of_transcripts_in_gene | Percent_of_transcripts_affected
Gene_Name | Gene_ID | Number_of_transcripts_in_gene | Percent_of_transcripts_affected

```{bash}
head GRCh37_BLB/ClinVar_GRCh37_BLB_Tx1_20240107.query.tsv
```

```{r}
tsv_ann <- read_tsv(
  "GRCh37_BLB/ClinVar_GRCh37_BLB_Tx1_20240107.query.tsv",
  col_names = c("chr", "start", "ref", "alt", "key", "ANN", "LOF", "NMD")
)

# 120,265
```

```{r}
tsv_ann_sep1 <- tsv_ann %>%
  separate_rows(ANN, sep = ",")

# 895,766
```

```{r}
tsv_ann_sep2 <- tsv_ann_sep1 %>%
  separate(
    ANN,
    c(
      "Allele",
      "Annotation",
      "Annotation_Impact",
      "Gene_Name",
      "Gene_ID",
      "Feature_Type",
      "Feature_ID",
      "Transcript_BioType",
      "Rank",
      "HGVSc",
      "HGVSp",
      "cDNA",
      "CDS",
      "AA",
      "Distance",
      "INFO"
    ),
    sep = "\\|", remove = T, convert = F
    )

# 895,766
```

```{r}
tsv_ann_sep2[tsv_ann_sep2 == ""] = "."
```

```{r}
df_ClinVar_GRCh37_BLB_snpeff_ensembl <- tsv_ann_sep2 %>%
  select(
    key, chr, start, ref, alt,
    Gene_Name, Gene_ID, Annotation, Annotation_Impact,
    Feature_ID, Feature_Type, Transcript_BioType,
    Rank, cDNA, CDS, AA, Distance,
    HGVSc, HGVSp,
    LOF, NMD
  ) %>%
  separate_rows(Feature_ID, sep = "-") %>%
  mutate(ENST = str_extract(Feature_ID, '[^\\.]+'))
```


```{r}
rm(tsv_ann, tsv_ann_sep1, tsv_ann_sep2)
```

---

# 濾掉怪Feature_ID
```{r}
df_ClinVar_GRCh37_BLB_snpeff_ensembl <- df_ClinVar_GRCh37_BLB_snpeff_ensembl %>%
  filter(str_detect(Feature_ID, '^ENS\\w\\d+')) %>%
  mutate(ENST = str_extract(Feature_ID, 'ENS\\w\\d+'))
```

```{r}
df_ClinVar_GRCh37_BLB_snpeff_ensembl %>%
  mutate(ENST = str_extract(ENST, 'ENS\\w')) %>%
  select(ENST) %>%
  group_by(ENST) %>%
  count()
```

---

```{r}
save(df_ClinVar_GRCh37_BLB_snpeff_ensembl, file = "GRCh37_BLB/df_ClinVar_GRCh37_BLB_snpeff_ensembl.RData")
```











